Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-21 demystify.tex
updates

The document might not be sufficient for students aiming for top-10 schools, which typically have different requirements\footnote{e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU}.  However, the information here should be useful for students aiming for other good schools, e.g., R1 institutions in the US. It is definitely useful for students aiming for GMU :)

>>>>

While this document may not fully meet the needs of students aiming for top-10 schools, which typically have more stringent requirements (e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU), it should be valuable for those targeting other reputable institutions, such as R1 universities in the US. It is certainly useful for students aiming for GMU!
